X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}

### 2013-09-11 hedpc_natphys.tex
New cover letter, dark-field description and SEM caption

In the past, a lot of effort has been invested into the development of
techniques which are sensitive to the phase shift. Since most of the
available phase contrast techniques rely on interference and thus typically
on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
sensitivity, practical applicability or achievable resolution. The vast
majority of the methods, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Techniques which are compatible with
an X-ray beam of low temporal coherence (broad bandwidth) are the inline
phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
apertures \cite{Munro2012}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the scatter strength of details in the sample\cite{Pfeiffer2008}.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
570$ and thus sufficiently attenuates X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and scanning electron microscope
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The interrupting bridges used for stabilizing the grating
        in the lithographic process can be seen with the SEM\cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@

%Fig. 3 shows a radiographic image of a metal screw in all three contrast
%modes, acquired with the $\SI{100}{\kilo\electronvolt}$ setup. The images
%were acquired in scanning mode, using a step size of $\SI{100}{\micro
%\metre}$. The number of phase steps was 24 and the exposure time was 15
%seconds per step. Grating interferometry at such a high diagnostic energy
%allows to examine more dense materials such as metals in phase contrast
%mode. At lower energies, the phase shifts of such materials would be too
%large and wrap over multiple periods of the analyzer grating.

>>>>

In the past, a lot of effort has been invested into the development of
techniques which are sensitive to the phase shift. Since most of the
available phase contrast techniques rely on interference and thus typically
on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
sensitivity, practical applicability or achievable resolution. The vast
majority of the methods, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Techniques which are compatible with
an X-ray beam of low temporal coherence (broad bandwidth) are the inline
phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
apertures \cite{Munro2012}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the integrated local small angle scattering power
from microscopic density fluctuations in a specimen\cite{Pfeiffer2008}.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Figure~\ref{Fig:grating_mask}. Each grating resides on a
silicon chip and has its specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy \cite{David2002}. Using
gold as the phase shifting material, this requires a structure length of
$h_1 = \SI{19.8}{\micro \metre}$. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter \cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$, this grating has an aspect ratio of $2h/p \approx
570$ and thus sufficiently attenuates X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. Beam splitter- and analyzer grating are
separated at the first fractional Talbot order \cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources \cite{Pfeiffer2006}. It is also made of gold structures
with a structure length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure} [ht]
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and scanning electron microscope
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The SEM image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing\cite{Kenntner2010}.}
        \label{Fig:grating_mask}
\end{figure}

@@
